Gafo-cc data processing

### 2023-05-31 analysis/gafo-cc-data-processing.Rmd
try running cv on cluster

# Leipzig

@@

```{r demographics}
raw_demographics_leipzig <- bind_rows(
  read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/docs/Gafo-cc-leipzig-participants.xlsx", sheet = 1)
  #read_xlsx("../../raw_data/gafo-cc/leipzig/Gafo-cc-leipzig-participants.xlsx", sheet = 1)
  )

tidy_demographics_leipzig <- raw_demographics_leipzig %>% 
  mutate(
    test_date = as.Date(test_date, format = "%d/%m/%Y"),
    birth_date = as.Date(birth_date, format = "%d.%m.%Y"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
  ) %>%
  select(-c(first_name, last_name, id, test_date, birth_date))%>%
  rename(subjid = code)%>%
  filter(status == "keep")
```

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"), 
  ) %>%
  mutate(subjID =as.factor(subjID))%>%select(-touchScreen)%>%
  distinct(subjID, trialNr, .keep_all = T)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)

@@

tidy_data_plymouth%>%
  filter(trialType == "test")%>%
  summarise(n = n_distinct(subjID))
```

```{r demographics}
raw_demographics_plymouth <- bind_rows(
  read_xlsx("../../raw_data/gafo-cc/plymouth/participants_information.xlsx", sheet = 1)
  )

test_date_plymouth <- tidy_data_plymouth%>%
  select(subjID, timestamp)%>%
  mutate(test_date = as.Date(substr(timestamp, 1,10),format = "%Y-%m-%d"))%>%
  select(-timestamp)%>%
  rename_all(tolower)

tidy_demographics_plymouth <- raw_demographics_plymouth %>% 
  select(-test_date)%>%
  left_join(test_date_plymouth)%>%
  mutate(
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
    younger_children = ifelse(younger_children == "N/A", NA, younger_children),
    younger_children = as.numeric(younger_children)
  )  %>%
  select(-c(test_date, birth_date, comment))%>%
  filter(!is.na(ageinyears))
```
```{r}
data_plymouth <- tidy_demographics_plymouth%>%
  left_join(tidy_data_plymouth%>%rename_all(tolower),by = c("subjid"))%>%
  distinct(subjid, trialnr, .keep_all = TRUE)

data_plymouth%>%
  #mutate(age_group = substr(ageinyears, 1,1))%>%
  #group_by(age_group)%>%
  summarise(n = n_distinct(subjid))

data_plymouth%>%
  group_by(subjid)%>%
  summarise(n())

@@

data_mex%>%summarise(n = n_distinct(subjid))
```

@@

@@

data <- bind_rows(
  data_zambia,
  data_namibia%>%rename(younger_children = youngerchildren),
  data_leipzig,
  data_nigeria,
  data_plymouth,
  data_stanford,
  data_mex,
  data_china
)%>%
  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
  filter(trialtype == "test")%>%
  mutate(age_group = substr(ageinyears, 1,1))

@@

data%>%
  filter(touchscreen == 2)
```

```{r}
data_plymouth%>%
  summarise(n= n_distinct(subjid))

>>>>

1^# Leipzig

@@

```{r demographics}
raw_demographics_leipzig <- bind_rows(
  read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/docs/Gafo-cc-leipzig-participants.xlsx", sheet = 1)
  #read_xlsx("../../raw_data/gafo-cc/leipzig/Gafo-cc-leipzig-participants.xlsx", sheet = 1)
  )%>%
  mutate(status = ifelse(code == "o9qVPfZD", "keep", status))

tidy_demographics_leipzig <- raw_demographics_leipzig %>% 
  mutate(
    test_date = as.Date(test_date, format = "%d/%m/%Y"),
    birth_date = as.Date(birth_date, format = "%d.%m.%Y"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
    sex = ifelse(sex == "w", "f", sex)
  ) %>%
  select(-c(first_name, last_name, id, test_date, birth_date))%>%
  rename(subjid = code)%>%
  filter(status == "keep")
```

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali")
  ) %>%
  mutate(subjID = ifelse(grepl("2023-03-11T19:4", timestamp) & subjID == "uksch048", "uksch049", subjID))%>%
  mutate(subjID =as.factor(subjID))%>%
  select(-touchScreen)%>%
  mutate_if(is.character, as.factor)%>% 
  distinct(subjID, trialNr, .keep_all = T)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)

unique(raw_data_plymouth$subjID)
```

@@

tidy_data_plymouth%>%
  filter(trialType == "test")%>%
  summarise(n = n_distinct(subjID))

tidy_data_plymouth%>%
  filter(subjID == "uksch048")
```

```{r demographics}
raw_demographics_plymouth <- bind_rows(
  read_xlsx("../../raw_data/gafo-cc/plymouth/participants_information_updated_2023_May.xlsx", sheet = 1)
  )%>%
  filter(tested == "yes")

test_date_plymouth <- tidy_data_plymouth%>%
  select(subjID, timestamp)%>%
  mutate(test_date = as.Date(substr(timestamp, 1,10),format = "%Y-%m-%d"))%>%
  select(-timestamp)%>%
  rename_all(tolower)%>%
  distinct(subjid, test_date)

tidy_demographics_plymouth <- raw_demographics_plymouth %>% 
  select(-test_date)%>%
  left_join(test_date_plymouth)%>%
  mutate(
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
    younger_children = ifelse(younger_children == "N/A", NA, younger_children),
    younger_children = as.numeric(younger_children)
  )  %>%
  select(-c(test_date, birth_date, comment))%>%
  filter(!is.na(ageinyears))

```{r}
data_plymouth <- tidy_demographics_plymouth%>%
  left_join(tidy_data_plymouth%>%rename_all(tolower),by = c("subjid"))%>%
  distinct(subjid, trialnr, .keep_all = TRUE)

data_plymouth%>%
  #mutate(age_group = substr(ageinyears, 1,1))%>%
  group_by(age)%>%
  summarise(n = n_distinct(subjid))

data_plymouth%>%
  group_by(age)%>%
  summarise(n())

@@

data_mex%>%summarise(n = n_distinct(subjid))

```
```{r}
# data_liz <- bind_rows(data_mex%>%
#   filter(trialtype == "test", voiceover == F)%>%
#   mutate(click_distance = abs(clickdistfromtargetcenterx))%>%
#   select("subjid" ,"community" ,"ageinyears" , "trialnr", "targetposition",  "click_distance", "sex", "economical_activity_dad" , "economical_activity_mom"   ,    "parents_education_level_dad"  , "parents_education_level_mom" ,  "income" ,    "screen"           ,             "touchscreen"       ,            "household"     ,                "children" ,
#         "younger_children"),
# 
# data_leipzig%>%
#   filter(trialtype == "test", voiceover == F)%>%
#   mutate(click_distance = abs(clickdistfromtargetcenterx))%>%
#   select("subjid" ,"community" ,"ageinyears" , "trialnr", "targetposition",  "click_distance", "sex", "screen"           ,             "touchscreen"       ,            "household"     ,                "children" ,
#         "younger_children")
# )
# 
# 
#   write_csv(data_liz, "../data/gafo-cc-data-lizbeth.csv")
#   
# 
# data_liz <- read_csv("gafo-cc-data-lizbeth.csv")
# 
# 
# data_liz_agg <- data_liz%>%
#   group_by(subjid, community, ageinyears, sex, economical_activity_dad, economical_activity_mom, parents_education_level_dad, parents_education_level_mom, income, screen, touchscreen, household, children, younger_children)%>%
#   summarise(mean_distance = mean(click_distance))%>% # aggregate data to get average click distance
#   ungroup()%>%
#   mutate(mean_distance_scale = scale(mean_distance, scale = F, center = T), # make the DV so that it has a mean of 0
#          z_ageinyears = scale(ageinyears, scale = F, center = T), # scale numeric variables
#          f_income = factor(income),# convert numeric variable into a factor because different values represent different categories
#          z_household = scale(household)) 
# 
# 
# library(lme4)
# 
# m1 <- lm(mean_distance_scale ~ z_ageinyears + community, data = data_liz_agg)
# 
# drop1(m1, test = "Chisq") # to get p-values for entire factors you need to use drop1
# 
# summary(m1)
```

@@

# Argentina

```{r read_data}
# get all .json files
files <- list.files("../../../../../../Cloud/QuantEx/Gafo-cc/data/argentina/", pattern = "*.json",recursive = T)

# convert json files to tibbles
raw_data_arg <- tibble()
for (f in files) {
  jf <- paste("../../../../../../Cloud/QuantEx/Gafo-cc/data/argentina/", f, sep = "")
  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))

  raw_data_arg <- bind_rows(raw_data_arg, jd)
}
# remove variables that we don't need anymore
rm(f, files, jf, jd)
```

```{r}
tidy_data_arg <- raw_data_arg %>%

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"),
  ) %>%select(-touchScreen)#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
```

```{r}
tidy_data_arg%>%
  summarise(n = n_distinct(subjID))

tidy_data_arg%>%
  group_by(subjID)%>%
  summarise(n = n())
```

```{r demographics}
raw_demographics_arg <- bind_rows(
  read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/argentina/gafo-cc-arg-participants.xlsx", sheet = 1, 
            col_types = c("text", "text", "text", "text", "date", "date", "text", "text", "text", "numeric", "numeric", "numeric", "numeric", "numeric", "text"))
  )

tidy_demographics_arg <- raw_demographics_arg %>% 
  filter(touchscreen!= "null")%>%
  mutate(
    test_date = as.Date(test_date, format = "%d/%m/%Y"),
    birth_date = as.Date(birth_date, format = "%d/%m/%Y"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25)
  )  %>%
  #filter(status == "keep")%>%
  select(-c(test_date, birth_date, comment, Edad))%>%
  rename(subjid = id)%>%
  filter(!is.na(ageinyears))%>%
  mutate(touchscreen = as.numeric(touchscreen),
         household = as.numeric(household),
         children = as.numeric(children),
         younger_children = as.numeric(younger_children))

tidy_demographics_arg%>%
  filter(ageinyears < 0)
```

```{r}
data_arg <- tidy_demographics_arg%>%
  left_join(tidy_data_arg%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(community = "buenos_aires")%>%
  distinct(subjid, trialnr, .keep_all = TRUE)
```

@@

data <- bind_rows(
  data_zambia,
  data_namibia%>%rename(younger_children = youngerchildren),
  data_leipzig,
  data_nigeria,
  data_plymouth,
  data_stanford,
  data_mex,
  data_china, 
  data_arg
)%>%
  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
  filter(trialtype == "test")%>%
  mutate(age_group = substr(ageinyears, 1,1), 
         trialnr = as.numeric(factor(trialnr)))%>%
  select(subjid, community, age_group, ageinyears, sex, screen, touchscreen, household, children, younger_children, trialnr, targetposition, targetcentralityx, clickdistfromtargetcenterx)%>%
  filter(ageinyears > 1)

@@

data%>%
  #group_by(community)%>%
  summarise(n = n_distinct(subjid))
```

```{r}
data%>%
  filter(touchscreen == 2)%>%
  distinct(subjid)

unique(data$screen)

unique(data$touchscreen)

unique(data$household)

unique(data$children)

unique(data$younger_children)
```

```{r}
data_arg%>%
  summarise(n= n_distinct(subjid))
